Predicting Success of Motivational Interviews with Recurrent Neural Network and Probabilistic Model for Patient-Provider Communication Sequences

### 2017-09-15 paper-amia-summit-2018/amia_summit_2018.tex
update embedding figure

\textbf {Embedding}: We took the inspiration for the representation of behavior codes from the idea of word embedding \cite{bengio2003neural}. Word embedding is a representation of words in low-dimensional space by vectors which contain the feature of the words. In our study, we employed embedding in place of one-hot vectors for the representation of behavior code since one-hot vectors are high-dimensional and sparse. Moreover, code embeddings have the ability to represent semantically similar codes with similar vectors in a low-dimensional space by retaining their internal relations. The embedding was learned during the training of the RNN model. Figure~\ref{fig:code_embedding} illustrates the myscope code embedding in 44-dimensional vector space visualize with t-SNE, a sophisticated technique for visualizing high-dimensional data. It can be seen that positive behavior codes such as OQECHT+, OQECML+, AF, AFL, SUP, RCML+S, CQECML+, etc. formed a cluster which is highlighted in the left part of the figure. However, right part of the figure demonstrates another cluster formed with negative behavior codes including CQECML-, AMB-, RCHT-C, OQECHT-, GINFO-, RBAC, LUP-, RCHT-S, RPTBC, RAMBC, AMB-, RCML-S, etc. because they are semantically similar in the low dimensional vector space.

\begin{figure}[!htb]
    \centering
    \includegraphics[width=0.50\textwidth]{figures/word_embed_highlighted.eps}
    \caption{\textbf{T-SNE diagram of behavior code drawn after 4000 steps with perplexity 30}.}
    \label{fig:code_embedding}
\end{figure}

>>>>

\textbf {Embedding}: We took the inspiration for the representation of behavior codes from the idea of word embedding \cite{bengio2003neural}. Word embedding is a representation of words in low-dimensional space by vectors which contain the feature of the words. In our study, we employed embedding in place of one-hot vectors for the representation of behavior code since one-hot vectors are high-dimensional and sparse. Moreover, code embeddings have the ability to represent semantically similar codes with similar vectors in a low-dimensional space by retaining their internal relations. The embedding was learned during the training of the RNN model. Figure~\ref{fig:code_embedding} illustrates the myscope code embedding in 44-dimensional vector space visualize with t-SNE, a sophisticated technique for visualizing high-dimensional data. It can be seen that positive behavior codes such as OQECHT+, OQECML+, AF, AFL, SUP, RCML+S, CQECML+, etc. formed a cluster which is shown in the left part of the figure. The nearest neighbors of CQECML+ are also highlighted by their color intensity i.e. OQECML+ is more purple means closer to CQECML+. However, right part of the figure demonstrates another cluster formed with negative behavior codes including CQECML-, AMB-, RCHT-C, OQECHT-, GINFO-, RBAC, LUP-, RCHT-S, RPTBC, RAMBC, AMB-, RCML-S, etc. because they are semantically similar in the low dimensional vector space.

\begin{figure}[!htb]
    \centering
    \includegraphics[width=0.50\textwidth]{figures/code_embed.eps}
    \caption{\textbf{T-SNE diagram of behavior code drawn after 4000 steps with perplexity 30}.}
    \label{fig:code_embedding}
\end{figure}
